Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
lay out structure of conclusions

@@

\section{Conclusions}
In conclusion, this paper has successfully achieved its objectives.
It has provided a comprehensive explanation of why real-world puzzles
present greater challenges compared to their digital counterparts.
Additionally, it has been shown that the same algorithm can have drastically worse
performance when working with real-world puzzles compared to digital ones.

>>>>

\section{Conclusions}
This section will conclude the paper,
by answering the two questions posed in \cref{document:objective}:

\begin{itemize}
  \item What is the difference in execution time between
                digital and real-world puzzles?
  \item What are the challenges to use the current state of the art algorithms developed for digital
                puzzles in the real-world, and how can we overcome them?
\end{itemize}
And by making some consideration about possible future works related to this problem.

\subsection{Difference In Execution Time}

\subsection{Applying Already Existing Algorithms To The Real World}

\subsection{Future Works}

\subsubsection{Machine Learning Based Comparator}

\subsubsection{Labeling tool}

\subsection{Conclusion}

@@

\section{ConclusionsOld}
In conclusion, this paper has successfully achieved its objectives.
It has provided a comprehensive explanation of why real-world puzzles
present greater challenges compared to their digital counterparts.
Additionally, it has been shown that the same algorithm can have drastically worse
performance when working with real-world puzzles compared to digital ones.
